% GitHub Repo and Documentation: https://github.com/celiobjunior/resume-template
% Copyright © 2025 Celio B Junior. All rights reserved.
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
% http://www.apache.org/licenses/LICENSE-2.0
%
% This template follows best practices from README.md

% Start of LaTeX document: defines document type and format
% a4paper = A4 page size, 10pt = base font size
\documentclass[a4paper,10pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{titlesec}
% For better line breaks in long URLs (don't use \href{}, use \url{} for long URLs)
% \usepackage{xurl}

% --- DOCUMENT SETUP ---
% Set page margins to maximize content space
\geometry{top=1.0cm, bottom=1.0cm, left=1.0cm, right=1.0cm}

% Remove page numbers and headers for clean resume look
\pagestyle{empty}

% PDF metadata - customize with your information
\hypersetup{
pdftitle={CV Caio Barbieri },
pdfauthor={ Caio Barbieri },
colorlinks=true,
linkcolor=black,
urlcolor=black,
citecolor=black,
bookmarksdepth=1
}

% Disable section numbering for cleaner appearance
\setcounter{secnumdepth}{0}

% Format section headers with bold text and underline
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}
[\titlerule\vspace{0.5ex}]

% --- BEGIN DOCUMENT ---
\begin{document}

% --- HEADER ---
% Replace with your personal information
\begin{center}
{\LARGE \textbf{ Caio Barbieri }}
\\ [0.1cm]
Campinas, São Paulo, Brazil
{\textbullet}
Email: \href{mailto:caio@lombello.com }{ caio@lombello.com }
{\textbullet}
\href{ https://linkedin.com/in/caiolvbarbieri }{linkedin.com/in/caiolvbarbieri }
{\textbullet}
\href{ https://github.com/caiolombello }{github.com/caiolombello }
\end{center}

% --- SECTIONS ---

\section{ Professional Experience }
% List work experience in reverse chronological order (most recent first)
\subsection*{\texorpdfstring{
\textbf{ Opsteam } \hfill 
}{
Opsteam -- 
}}
\textit{ SRE | Cloud Engineer \hfill Ago 2025 - Presente }
\begin{itemize}
\item Providing specialized services in Site Reliability Engineering (SRE) and Cloud, with a focus on managing infrastructure in AWS and other cloud providers.
\item Implementing reliability, automation, and observability practices to ensure resilience, security, and efficiency.
\item Supporting DevOps initiatives and technical consulting for clients, promoting best practices in architecture and governance within Cloud Native environments.
\end{itemize}
\subsection*{\texorpdfstring{
\textbf{ Vertigo Tecnologia } \hfill 
}{
Vertigo Tecnologia -- 
}}
\textit{ Senior DevOps Analyst \hfill Jun 2025 - Ago 2025 }
\begin{itemize}
\item Responsible for architecting and delivering the entire platform engineering foundation for an enterprise client.
\item Created reusable templates and modules with IaC, DevSecOps pipelines using ArgoCD, integration with Keycloak and Backstage, and deployed a centralized, multi-cluster observability stack.
\item Managed Kubernetes environments across multiple clouds (AWS and Oracle Cloud), ensuring secure, scalable, and standardized operations.
\item Technically led the project, executing all implementations hands-on.
\end{itemize}
\subsection*{\texorpdfstring{
\textbf{ Vertigo Tecnologia } \hfill 
}{
Vertigo Tecnologia -- 
}}
\textit{ Mid-level DevOps Analyst \hfill Set 2024 - Jul 2025 }
\begin{itemize}
\item Developed infrastructure automation solutions and CI/CD pipelines for various clients.
\item Led AI-based automation initiatives and actively contributed to the VeeCode platform by creating templates, plugins, and custom features.
\item Implemented observability solutions and provided ongoing DevOps consulting to support digital transformation and team enablement.
\end{itemize}
\subsection*{\texorpdfstring{
\textbf{ Vertigo Tecnologia } \hfill 
}{
Vertigo Tecnologia -- 
}}
\textit{ Junior DevOps Analyst \hfill Oct 2022 - Sep 2024 }
\begin{itemize}
\item Led Cloud Native cultural transformation initiatives, developed GitOps/DevSecOps pipelines with Bamboo and Shell Script, and implemented monitoring stacks with Grafana, Prometheus, Loki, and Alertmanager.
\item Managed Redis, RabbitMQ, custom Helm Charts, Dockerfiles, and local clusters with K3d.
\item Created Terraform automations and reinforced AWS security by applying the principle of least privilege.
\item Also managed HashiCorp's Vault and Consul, ensuring security and resilience in secret and network management.
\end{itemize}
\subsection*{\texorpdfstring{
\textbf{ Vertigo Tecnologia } \hfill 
}{
Vertigo Tecnologia -- 
}}
\textit{ DevOps Intern \hfill Feb 2022 - Oct 2022 }
\begin{itemize}
\item Implemented GitLab on a DigitalOcean cluster using Helm and Kubernetes.
\item Automated the migration of over 200 repositories via Python and the GitLab API.
\item Optimized Helm templates, CI/CD pipelines, and containerized applications to accelerate the development cycle.
\end{itemize}

% ------

\section{ Skills }
% Keep this section concise and relevant to your target jobs
\begin{itemize}
\item \textbf{ Cloud/Infra: } AWS, Oracle Cloud, Kubernetes, Terraform, HashiCorp Consul
\item \textbf{ Containerization: } Docker
\item \textbf{ CI/CD: } GitOps, DevSecOps, Helm, ArgoCD
\item \textbf{ Languages: } Python, Golang
\item \textbf{ Observability: } Prometheus, Grafana, OpenTelemetry, Tempo, Loki, Thanos, Alertmanager
\item \textbf{ Security: } HashiCorp Vault, Keycloak
\item \textbf{ Tools: } Backstage
\item \textbf{ Automation: } LLMs
\end{itemize}

% ------

\section{ Education }
% Use this format for each degree - most recent first
\subsection*{\texorpdfstring{
\textbf{ Universidade Estácio de Sá } \hfill 
}{
Universidade Estácio de Sá -- 
}}
\textit{ Bachelor in Information Systems \hfill Mar 2022 - Dez 2025 }

\end{document}
